Generate data for multispecies modeling, including diet!

### 2020-08-04 NOBAmsdiets.Rmd
call new om_species with diet

@@

NOBAom <- om_init(here("config/NOBA2config.R"))

NOBAom_ms <- om_species(sppsubset$Name, NOBAom)

>>>>

### Total consumption time series

The true data can be generated without updated config files (once I fix missing diets in wrappers!):

```{r OMtruth}

NOBAom <- om_init(here("config/NOBA2config.R")) #run and saved June 19,
# run again 3 August to update biomass_eaten

#NOBAom_ms <- om_species(sppsubset$Name, NOBAom) #run and saved June 19
# run again 3 August to test new wrapper that should save biomass_eaten
NOBAom_ms <- om_species(sppsubset$Name, NOBAom, diet=TRUE)

#source(here("config", "NOBA2config.R"))

# diet data are not in here, need to revise wrapper
#NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))

# get from full truth run--big file
#truth <- get(load(file.path(d.name,
#                                paste0(scenario.name, "run_truth.RData"))))

# questions: does biomass_eaten have some diet comp info as dietcheck.txt?
# load dietcheck with om_init using a switch in config file?
# add or pass along switch to keep biomass_eaten truth output in species file
# is biomass_eaten correct?
#   revised load_diet_comp to *not include* NAs that merge poorly
# polygon specific total mg N consumed per unit volume times volume of polygon
# then split to prey using global diet fraction (and converted to t)

#bioeaten_ss <- truth$biomass_eaten %>%
#  filter(species %in% sppsubset$Name)

# compare ms_diet$atoutput to bioeaten_ss$dietfrac
# should match for species, agecl, time.days, prey

@@

#NOBAom <- om_init(here("config/NOBA2config.R"))

#NOBAom_ms <- om_species(sppsubset$Name, NOBAom)

NOBAom_ms <- readRDS(file.path(d.name, paste0(scenario.name, "omlist_ss.rds")))
